A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
A radical reordering

\iffalse
\paragraph{Heuristics} We ran a small experiment comparing lots of heuristics
such as \dots on random instances. The one where you choose a label class with
as small a max(left size, right size) as possible seemed to work best. ? Why?
\fi

\section{Comparison with Existing Algorithms}\label{sec:comparison} The
\McSplit\ algorithm may be considered as a version of the constraint
programming, forward-checking (CP-FC) algorithm of
\citep{DBLP:conf/cp/NdiayeS11}, using an efficient, compressed representation
of domains.  In the CP-FC algorithm, each vertex in $v \in \V(G)$
is represented by a variable, whose domain corresponds to the set of vertices
in $\V(H)$ to which $v$ may currently be mapped.

Given a label class $\langle P,T \rangle$ in \McSplit\, the vertices in $P$
correspond to variables in CP-FC, all of which have domain equal to $T$.  The
label-class representation of domains is possible because throughout the CP-FC
algorithm for max common subgraph, the domains of any two variables are either
identical or disjoint.  (To the best of our knowledge, this observation has
not been made previously.)

? Mention partition backtracking

\section{Extensions}\label{sec:extensions}

@@

>>>>

\subsection{Heuristics}

?? Heuristics go here, defer justification until \cref{sec:comparison}

\subsection{Extensions}\label{sec:extensions}

@@

\section{Comparison with Existing Algorithms}\label{sec:comparison} The
\McSplit\ algorithm may be considered as a version of the constraint
programming, forward-checking (CP-FC) algorithm of
\citet{DBLP:conf/cp/NdiayeS11}, using an efficient, compressed representation
of domains.  In the CP-FC algorithm, each vertex in $v \in \V(G)$ is
represented by a variable, whose domain corresponds to the set of vertices in
$\V(H)$ to which $v$ may currently be mapped, with an additional special $\bot$
value representing an unmapped vertex.

Given a label class $\langle P,T \rangle$ in \McSplit\, the vertices in $P$
correspond to variables in CP-FC, all of which have domain equal to $T \cup \{
    \bot \}$.  The label-class representation of domains is possible because
throughout the CP-FC algorithm for max common subgraph, the domains of any two
variables are either identical or disjoint.  (To the best of our knowledge,
this observation has not been made previously.)

?? Mention partition backtracking

?? Mention dual viewpoint heuristics
